Review of Group 9 by Group 1

### 2015-03-18 rmtw/a4_review/latex8.tex
Made some small changes to a4 review

\Section{Introduction}
The text for Section I and II are good, and fit the purpose of the sections. We chose to copy and paste the same part from Richard's pdf. The formatting of the sections could be improved, however. The overall structure of the paper is good, but it has some minor issues.

@@

\section{Writing and Structure}​​
​​The two first paragraphs of Section III don't really apply to this study. It seems to be more of a general explanation of why and when one should perform a statistical analysis.

@@

>>>>

@@

\section{Writing and Structure}​​
The title of the paper should probably be copied from Richard's Experiment\_Design.pdf. The text for Section I and II are good, and fit the purpose of the sections. We chose to copy the same part from Richard's pdf. The formatting of the sections could be improved, however. The overall structure of the paper is good, but it has some minor issues.

​​The two first paragraphs of Section III don't really apply to this study. It seems to be more of a general explanation of why and when one should perform a statistical analysis.

@@

There are quite a few grammatical errors in the text, so you should probably read through it again and think of where you can improve the phrasing. We found no spelling errors.
